---
title: "HW Assignment 04"
author: "Richard Hart"
date: "February 2, 2019"
output: 
  html_document:
    keep_md: true
---

## Questions

### 1. Harry Potter

  Loading Libraries
  
```{r, echo=TRUE}
library(tidyr)
library(rvest)
library(dplyr)
```

a. View the Table data at the link below:
```{r, eval=FALSE, echo=TRUE}
http://www.imdb.com/title/tt1201607/fullcredits?ref_=tt_ql_1
```

b. Scraping the Cast information from the URL above:
```{r, echo=TRUE}
cast <- read_html("http://www.imdb.com/title/tt1201607/fullcredits?ref_=tt_ql_1")
cast_list <- cast %>% html_nodes(xpath = '//*[@id="fullcredits_content"]/table[3]') %>% html_table(header = TRUE)
cast_df <- cast_list[[1]]
```

c. Cleaning up the Table

  * Labeling and Removing the Unnecessary Columns
```{r, echo=TRUE}
colnames(cast_df) <- c("1", "Actor", "2", "Character")
cast_df = select(cast_df, "Actor", "Character")
```

  * Update Mr. Warwick's Character Name
```{r, echo=TRUE}
cast_df$Character[10] <- 'Griphook / Professor Filius Flitwick'
```

  * Removing the row that contains "Rest of cast listed alphabetically" which is found at row 92
```{r, echo=TRUE}
cast_df <- cast_df[-c(92), ]
```

d. Splitting Actor Name into First and Last Names
```{r, echo=TRUE}
cast_df <- cast_df %>% separate(Actor, c("FirstName", "SurName"), "(?=[^ ]+$)", extra = "merge" )
```

e. Present the first 10 rows
```{r, echo=TRUE}
head(cast_df, 10)
```

### 2. SportsBall

  Loading Libraries
  
```{r, echo=TRUE}
library(tidyr)
library(rvest)
library(dplyr)
```

a. View the Table data at the link below:
```{r, eval=FALSE, echo=TRUE}
http://www.espn.com/nba/team/stats/_/name/sa/san-antonio-spurs
```

b. Scraping the Shooting Statistic from the URL above:
```{r, echo=TRUE}
shoots <- read_html("http://www.espn.com/nba/team/stats/_/name/sa/san-antonio-spurs")
shoots_list <- shoots %>% html_nodes(xpath = '//*[@id="fittPageContainer"]/div[2]/div[5]/div[1]/div/article/div/section/section/section[2]/table') %>% html_table(fill = TRUE)
shoots_df <- shoots_list[[1]]
```

c. Cleaning up the Table

```{r, echo=TRUE}
# Remove Unwanted and Unnecessary Columns and Rows
shoots_df <- shoots_df[-c(1), ]
shoots_df <- shoots_df[-c(18), ]
shoots_df <- shoots_df[ , -c(15:258) ]
shoots_df <- shoots_df[-c(17), ]
shoots_df <- shoots_df[-c(33), ]

# Create a vector with the names of Players
name_vector <- as.vector(shoots_df$X1[2:16])

# Remove the Rows with the Names of the Players, I will add these back soon
shoots_df <- shoots_df[-c(1:16), ]

# Create a vector using the column names, which are not yet columns
col_vector <- as.character(shoots_df[1,])
# Append Name to the beginning of the vector made above
col_vector <- append(col_vector, "Name", after = 0)
shoots_df <- shoots_df[-c(1), ]

# Add the name vector as several rows to be row headings to the data frame
shoots_df <- cbind(name_vector, shoots_df)

# Add the column vector to data frame to be the column headings
colnames(shoots_df) <- col_vector

# Separate Team Position out into a column
shoots_df <- shoots_df %>% separate(Name, c("Name", "Position"), "(?=[^ ]+$)", extra = "merge")

# convert all but Name and Position to Numeric
shoots_df[3:16] <- sapply(shoots_df[3:16], as.numeric)
sapply(shoots_df, class)

# First 10 values of the data frame
head(shoots_df, 10)
```

d. Creating a Bar Chart
```{r, echo=TRUE}
colors <- RColorBrewer::brewer.pal(length(unique(shoots_df$Position)), name = "Set1")
shoots_df$color <- colors[as.factor(shoots_df$Position)]
par(las=2)
barplot(shoots_df$`FG%`, main = "San Antonio Spurs Player Field Goals Percentage Per Game", horiz = TRUE, xlab = "Field Goal % Per Game", col = shoots_df$color, names.arg = shoots_df$Name, cex.names = 0.7)
```
