---
title: "HW Assignment 03"
author: "Richard Hart"
date: "January 27, 2019"
output: html_document
---

# Homework Assignment 03

## Questions

### Question 1 Github Cloning

  * Make a new Directory
  
```{r, eval=FALSE, echo=TRUE}
    $ mkdir Git_Projects
```
  * Navigate to newly created directory
```{r, eval=FALSE, echo=TRUE}
    $ cd Git_Projects
```
  * Clone Repository to this nely created directory
```{r, eval=FALSE, echo=TRUE}
    $ git clone git@github.com:awesomedata/awesome-public-datasets.git
```
  
### Question 2 Data Summary

  a. Read in the titanic.csv
```{r, echo=TRUE}
getwd()
df <- read.csv(file = "Git_Projects/awesome-public-datasets/Datasets/titanic.csv", header=TRUE, sep=',')
```

  b. Female and Male Counts
```{r, echo=TRUE}
female_count <- sum(df$Sex == "female")
female_count
```

```{r, echo=TRUE}
male_count <- sum(df$Sex == "male")
male_count
```

```{r, echo=TRUE}
plot(df$Sex, xlab = "Sex", ylab = "Total Number of each Sex", main = "Frequency of Females and Males onboard the Titanic")
```

  c. Means of Age, Fare and Survival
```{r, echo=TRUE}
means_df <- data.frame(df$Age, df$Fare, df$Survived)
sapply(means_df, mean, na.rm = TRUE)
```

### Question 3 Function Building

```{r, echo=TRUE}
sleep_data_func <- function(x) {
  
  # Read in the csv to the data frame named sleep.
  sleep <- read.csv(file = x, header = TRUE, sep = ",")
  
  # A. Creating objects for median Age, the minimum and maximum Duration of sleep, 
  # and the mean and standard deviation of the Rosenberg Self Esteem scale (RSES).
  median_age <- median(sleep$Age, na.rm = TRUE)
  min_duration <- min(sleep$Duration, na.rm = TRUE)
  max_duration <- max(sleep$Duration, na.rm = TRUE)
  mean_rses <- mean(sleep$RSES, na.rm = TRUE)
  sd_rses <- sd(sleep$RSES, na.rm = TRUE)
  
  # B. This section creates a Data Frame containg the median age, the mean and sd of RSES, both
  # divided by 5, and range of the duration of sleep.
  report <- data.frame(median_age, mean_rses/5, sd_rses/5, max_duration-min_duration)
  
  # C. This secion sets the column names of the data frame.
  cols <- c("MedianAge", "SelfEsteem", "SE_SD", "DurationRange")
  colnames(report) <- cols
  
  # D. This section rounds the values in each column of the data frame to 2 digits.
  report <- round(report, 2)
  
  # E. Output the data frame.
  report
}
```

#### Function Output
```{r, echo=TRUE}
sleep_data_func("sleep_data_01.csv")
```

### Question 4 FiveThirtyEight Data

  a. Install Package
```{r, echo=TRUE}
#install.packages("fivethirtyeight", repos = "http://cran.us.r-project.org")
```

  b. Listing of the Datasets in FiveThirtyEight and assigning 22nd to df
```{r, echo=TRUE}
library(fivethirtyeight)
df <- college_recent_grads
```
  c. More detailed list of the datasets in FiveThirtyEight
```{r, echo=TRUE}
#vignette("fivethirtyeight", package = "fivethirtyeight")
#Url for the above is http://127.0.0.1:27980/library/fivethirtyeight/doc/fivethirtyeight.html
```
  

  d. Dimensions and column names of data frame.
```{r, echo=TRUE}
dim(df)
```
```{r, echo=TRUE}
colnames(df)
```

### Question 5 Data Summary
  a. Column Names
```{r, echo=TRUE}
colnames(df)
```

  Column Count
```{r, echo=TRUE}
ncol(df)
```

  b. major_count
```{r, echo=TRUE}
library(plyr)
major_count <- count(df, "major_category")
```

  c. Graph Frequency of College Majors from major_count
```{r, echo=TRUE}
par(las=2)
barplot(major_count$freq, main = "Frequncy of College Majors from Recent College Grads", horiz = TRUE, xlab = "Frequency", ylab = "College Major", col = c("blue", "blueviolet", "brown4", "chartreuse", "chocolate", "coral", "cyan4", "darkblue", "darkcyan", "darkorange", "darkorchid", "deepskyblue", "dodgerblue", "firebrick", "forestgreen", "maroon"), names.arg = major_count$major_category)
```

  d. Write df to csv
```{r, echo=TRUE}
write.csv(df, file = "Recent_College_Grads.csv", row.names = FALSE)
```

### Question 6 CodeBook
* Link to the my DS6306 HW Repo can be found:
    + https://github.com/rhart211/DS6306_HW
* Link to where this homework can be found:
    + https://github.com/rhart211/DS6306_HW/tree/master/HW3
