---
title: "Homework 5"
author: "Richard Hart"
date: "2/7/2019"
output: 
  html_document:
    keep_md: true
---

# Homework Assignment 5

### Question 1 Data Munging

Loading Libraries
```{r, echo=TRUE}
library(tidyr)
```

a. Importing, opening and creating a data frame from yob2016.txt file.
```{r, echo=TRUE}
df <- read.csv(file = "/Users/rhart/Dropbox/SMU Classes/6306 Doing DataScience/Homework/HW 5/yob2016.txt", header = FALSE, sep = ";")
```

b. Summary and Structure of df
```{r, echo=TRUE}
summary(df)
str(df)
```

c. Find the duplicate name that contains 3 y's
```{r, echo=TRUE}
grep('yyy', df$V1)
```

d. Remove the row that contains the duplicate name found in c.
```{r, echo=TRUE}
y2016 <- df[-grep('yyy', df$V1), ]
```

### Question 2 Data Merging

a. Importing, opening and creating a data frame from yob2015.txt file.
```{r, echo=TRUE}
y2015 <- read.csv(file = "/Users/rhart/Dropbox/SMU Classes/6306 Doing DataScience/Homework/HW 5/yob2015.txt", header = FALSE, sep = ",")
```

b. Display the 10 rows.
```{r, echo=TRUE}
tail(y2015, 10)
```

What's interesting about these last 10 rows is that they're all very similar to each other in spelling. For instance, the names Zykir, Xyrus, and Zyus are only a few letters different from each other.

c. Merge both y2015 and y2016 together by the name column.
```{r, echo=TRUE}
final <- merge(y2015, y2016, by = "V1")
```

### Question 3 Data Summary

a. Add a new "Total" column and the number of children for each year together
```{r, echo=TRUE}
final$Total <- final$V3.x + final$V3.y
```

b. Sort final by Total
```{r, echo=TRUE}
tail(final[order(final$Total), ], 10)
```

c. Top 10 Most Popular Girls' Names
```{r, echo=TRUE}
girls <- final[-grep('M', final$V2.x), ]
tail(girls[order(girls$Total), ], 10)
```

d. Write only the girls' names to CSV
```{r, echo=TRUE}
write.csv(girls[,c("V1", "Total")], file="MostPopularGirlsNames.csv",row.names=FALSE)
```

### Question 4 GitHub Location
```{r, eval=FALSE, echo=TRUE}
https://github.com/rhart211/DS6306_HW/tree/master/HW5
```